General:
% -	The title seems to use incorrect grammar, please fix
% -	There needs to be a section that explains neural networks, as in how they mathematically function, very important!
% This needs to include the concept of layers and layer types.
-	There also needs to be a section, or sub-section that explains neural network architecture, very important!
This should be done in terms of the mathematical explanation.
-	I would suggest separating review and discussion of architectures in general, from the description of the experiment you ran.

Introduction:
% -	This is a bit vague – can you start with explaining precisely what your work is about, and then discuss the relevant sub-topics more systematically?

Section 2:
% -	Related work, I’d consider part of the introduction section, e.g., as a literature review sub-section.
-	You need to be precise in identifying differences in applications (what is the NN used for?) and architectures (how is it built?)
-	Hardware is also an issue but maybe not that relevant to you?
-	What you also need to discuss, and review, is prior art that benchmarks architectures for given applications. This is important, as you need to review the state-of-art in what you do.

Coding:
-	I’d suggest separating custom contributions to the code from set-up of the experiment. Currently, some things I’d expect in the latter chapter are here.
-	Also, you don’t need to explicitly present all of your code. Better attach it, or provide a github link, and highlight only relevant parts if you need to.

Experiments:
-	Whenever you describe these, you need to list, and precisely describe: the contender models, and how they were trained/tuned; the performance metrics; the evaluation set-up, including data and re-sampling for performance estimation
-	There’s probably something wrong with he LRN layer, please check.
-	If you use dropout, you may have to adjust learning rates, please check. Not doing so would explain bad results.



- Intriduction - what is this about, related work
-
- Methodolody section,

- experiment

- results

- experiments
- literature , ARCHETRUTRE AND CODE S, MAKE SURE TO TALK ABOUT POTETIAL REASONS
- keras indroces and additional layer of abtrastion
explain  keras as a software framework
dropout
sgb epoch adn bactches
learning

